---
title: "markdown"
author: "HaiDao"
date: "30/10/2015"
output: html_document
---

---
title: "dcmarkdown"
output: html_document
---

##Introduction to plotting with ggplot2
```{r warning=FALSE, message=FALSE}
library(ggplot2)

library(dplyr)
```

##Step 2: Get the data we need
```{r}
surveys_raw <- read.csv('http://files.figshare.com/1919744/surveys.csv')
```

##Step 3: Clean up the data before plotting
```{r}
surveys_complete <- surveys_raw %>% filter(species_id != "")
```

#Remove empty weights and empty hindfoot lengths
surveys_complete <- surveys_raw %>% filter(species_id!="") %>%
                                filter(!is.na(weight)) %>%
                                filter(!is.na(hindfoot_length))


#Remove species with low counts
#Count number of records per species
species_counts <- surveys_complete %>%
                  group_by(species_id) %>%
                  tally

frequent_species <- species_counts %>%
                    filter(n>=10) %>%
                    select(species_id)

surveys_complete <- surveys_complete %>%
                    filter(species_id %in% frequent_species$species_id)


#Step 4: create a basic plot
plot (x=surveys_complete$weight, y=surveys_complete$hindfoot_length)